Spectroscopic confirmation of very-wide stellar binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-12-07 paper/comoving-followup.tex
remove galah

The information contained in a large sample of widely-separated, comoving star
pairs spans from the dynamics of stars and dark matter in the Galaxy, the
fundamentals of star formation, and the stability of planetary systems.
Through our own low-resolution spectroscopic follow-up and a cross-match with
the RAVE \DR{5} catalog, we have identified \ncomovingtotal\ comoving star pairs
by combining these radial velocity measurements with astrometry from the \tgas\
catalog.
From a cross-match to the \acronym{LAMOST} survey, we find that candidate
comoving star pairs with small differences in radial velocities also have small
differences in iron abundance, even at large separations ($>1~\pc$).
The separation distribution of the spectroscopically-confirmed comoving star
pairs presented shows an abundance of comoving pairs at separations between
$1$--$10~\pc$ (\figurename~\ref{fig:separation-scatter}), the imposed limit in
our initial search (\citealt{Oh:2017}).
\edits{Though there is likely contamination even in the sample of 3D comoving
star pairs identified in this work, the fact that other large-separation
($>1~{\rm pc}$, comoving star pairs in \acronym{LAMOST} and the \acronym{GALAH}
surveys (Simpson, et al., in prep.) have similar chemical properties suggests
that some fraction are real.}
This result is further evidence (see also \citealt{Shaya:2011}) for the
existence of a population of unbound comoving stars that represent the ultimate
fate of wide binaries and moving groups that slowly dissociate due to weak
perturbations from stars (\citealt{Jiang:2010}) and other massive perturbers in
the Galaxy.
\edits{We feel that this work justifies a concerted effort to obtain
high-resolution spectroscopic follow-up to use chemical information to identify
the largest-separation comoving pairs.}
From this work it appears that modeling the population of wide binaries or
comoving stars with a monotonically decreasing separation distribution---as is
commonly done---may be too simple to also represent the population of unbound
systems.
With future data releases from the \gaia\ mission combined with large
spectroscopic surveys, the anticipated catalogs of high-probability comoving
star pairs will offer a new ``stereo'' view on the evolution and state of our
Galaxy.

>>>>

The information contained in a large sample of widely-separated, comoving star
pairs spans from the dynamics of stars and dark matter in the Galaxy, the
fundamentals of star formation, and the stability of planetary systems.
Through our own low-resolution spectroscopic follow-up and a cross-match with
the RAVE \DR{5} catalog, we have identified \ncomovingtotal\ comoving star pairs
by combining these radial velocity measurements with astrometry from the \tgas\
catalog.
From a cross-match to the \acronym{LAMOST} survey, we find that candidate
comoving star pairs with small differences in radial velocities also have small
differences in iron abundance, even at large separations ($>1~\pc$).
The separation distribution of the spectroscopically-confirmed comoving star
pairs presented shows an abundance of comoving pairs at separations between
$1$--$10~\pc$ (\figurename~\ref{fig:separation-scatter}), the imposed limit in
our initial search (\citealt{Oh:2017}).
\edits{Though there is likely contamination even in the sample of 3D comoving
star pairs identified in this work, the fact that other large-separation
($>1~{\rm pc}$, comoving star pairs in \acronym{LAMOST} have similar chemical properties suggests that some fraction are real.}
This result is further evidence (see also \citealt{Shaya:2011}) for the
existence of a population of unbound comoving stars that represent the ultimate
fate of wide binaries and moving groups that slowly dissociate due to weak
perturbations from stars (\citealt{Jiang:2010}) and other massive perturbers in
the Galaxy.
\edits{We feel that this work justifies a concerted effort to obtain
high-resolution spectroscopic follow-up to use chemical information to identify
the largest-separation comoving pairs.}
From this work it appears that modeling the population of wide binaries or
comoving stars with a monotonically decreasing separation distribution---as is
commonly done---may be too simple to also represent the population of unbound
systems.
With future data releases from the \gaia\ mission combined with large
spectroscopic surveys, the anticipated catalogs of high-probability comoving
star pairs will offer a new ``stereo'' view on the evolution and state of our
Galaxy.
